---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Familias 2.6.1

Familias has existed since 2000 as a Windows program and can be downloaded from https://familias.no.
The program calculates likelihoods and probabilities used to infer family relationships based on autosomal marker data. The core code of the Windows program programmed in C++ has been available since 2012 in R. 
The mentioned website also contains references describing the implementation and validation.

No further development of this package is planned.
For forensic pedigree analyses and 
visualisations we rather recommend the `pedsuite` packages, see
https://magnusdv.github.io/pedsuite/. In particular, the package 
`pedFamilias` facilitates conversion of .fam files into the `pedsuite` format.

## Installation

Install from GitHub by as follows:
```{r, eval = FALSE}
 # First install devtools if needed
if(!require(devtools)) install.packages("devtools")

# Install Familias from GitHub
devtools::install_github("thoree/Familias")
```

